An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-05 scagnostics.Rmd
Added code for calculation time comparison, results not yet available.

@@

### Review of guided tour optimisation

We use the default method "search_geodesic" implemented in the tourr package. (Should I try other optimisation methods, i.e. search_better, search_better_random?)
Search geodesic first collects $n=5$ samples by default, amongst which the most promising direction is selected. In a second step a linear search along the geodesic is performed in that direction. The optimisation is stopped when ???

@@

### Note on calculation time
Considerations: time to calculate index for single 2-d plot, parameters to turn for guided tour (max.tries, alpha, cooling)

>>>>

## Note on calculation time
Computing time differs for each index, and depends strongly on the number of data points (as well as probably some dependence on distribution type), here we use as an example the 6-d sphere and calculate the computing time for different indices over 100 interpolated grand tour projections as a function of the sample size.

```{r getTimer}
timeThis <- function(d, t, idx, pmax){ #d=data matrix, t=interpolated tour path, idx=index function, pmax=max number of projections
    i <- 1
    tic.clearlog()
    tic() #start timer
    for(pMatrix in t){
      if(i>pmax) break
      dProj <- d %*% pMatrix
      sgnst <- idx(dProj[,1],dProj[,2])
      i = i+1
    }
    toc(log=TRUE,quiet=TRUE)
    scTd <- unlist(tic.log(format=FALSE))["toc.elapsed"]-unlist(tic.log(format=FALSE))["tic.elapsed"]
}

```

```{r timer}
if(!file.exists("cache/timer.rda")){
  set.seed(2018)
  grandTour100 <- save_history(sphere100, grand_tour(2), max=4) %>%
    interpolate() %>%
    as.list()

  sizeL <- seq(0,10000,by=100)
  n <- length(sizeL)
  dfTimer = data.frame( n=rep(0, n), scagT=rep(0,n), dcorT=rep(0,n), splineT=rep(0,n), mineT=rep(0,n))
  t <- 1
  for(sampleSize in sizeL){
    set.seed(sampleSize + 11) # new seed for each sample size
    if(sampleSize == 0) sampleSize = 10 # smallest considered sample has 10 points
    thisMatrix <-  sphereData(6, sampleSize) %>% rescale()
    scagT <- timeThis(thisMatrix, grandTour100, scagnostics.default, 100)
    dcorT <- timeThis(thisMatrix, grandTour100, dcor2d, 100)
    splineT <- timeThis(thisMatrix, grandTour100, splines2d, 100)
    mineT <- timeThis(thisMatrix, grandTour100, mine, 100)
    dfTimer[t,] <- c(sampleSize, scagT, dcorT, splineT, mineT)
    t <-  t+1
  }
  save(dfTimer, file = "cache/timer.rda")
} else {
  load("cache/timer.rda")
}

timerMelt <- melt(dfTimer, id="n")
ggplot(timerMelt, aes(x = n, y = value, color=variable)) + 
  geom_line() +
  geom_line(data=subset(df, n==2),aes(linetype = as.factor(n))) +
  geom_line(data=subset(df, n==3),aes(linetype = as.factor(n))) +
  labs(x = "Sample Size", y = "Time [s]", color = "Index family")
```

@@

@@
